---
title: "Bellabeats Casestudy"
author: "Gbemisola Famade"
date: "`r Sys.Date()`"
output: html_document
---

## Bellabeats Capstone Project - Google Data Analytics

##### Introduction :
Bellabeat Inc is a leading Silicon Valley Wellness Fem-tech business whose target audience are health-conscious individuals globally.
Women's health has always been the top priority for its founders Urska Srsen and Sandro Mur who founded the company in 2014. By 2016, Bellabeat had opened offices around the world and launched multiple products. Bellabeat products became available
through a growing number of online retailers in addition to their own e-commerce channel on their website. The company
has invested in traditional advertising media, such as radio, out-of-home billboards, print, and television, but focuses on digital
marketing extensively. Bellabeat invests year-round in Google Search, maintaining active Facebook and Instagram pages, and
consistently engages consumers on Twitter. Additionally, Bellabeat runs video ads on Youtube and display ads on the Google
Display Network to support campaigns around key marketing dates

##### Products :

+ Bellabeat app: The Bellabeat app provides users with health data related to their activity, sleep, stress,
menstrual cycle, and mindfulness habits. This data can help users better understand their current habits and
make healthy decisions. The Bellabeat app connects to their line of smart wellness products.

+ Leaf: Bellabeat’s classic wellness tracker can be worn as a bracelet, necklace, or clip. The Leaf tracker connects
to the Bellabeat app to track activity, sleep, and stress.

+ Time: This wellness watch combines the timeless look of a classic timepiece with smart technology to track user
activity, sleep, and stress. The Time watch connects to the Bellabeat app to provide you with insights into your
daily wellness.

+ Spring: This is a water bottle that tracks daily water intake using smart technology to ensure that you are
appropriately hydrated throughout the day. The Spring bottle connects to the Bellabeat app to track your
hydration levels.

+ Bellabeat membership: Bellabeat also offers a subscription-based membership program for users.
Membership gives users 24/7 access to fully personalized guidance on nutrition, activity, sleep, health and
beauty, and mindfulness based on their lifestyle and goals.

#### Act:

##### Business Task :

Analyze smart device usage data in order to gain insight into how consumers use non-Bellabeat smart devices.

##### Questions : 

+ What are some trends in smart device usage?

+ How could these trends apply to Bellabeat customers?

+ How could these trends help influence Bellabeat marketing strategy?

##### Key Stakeholders:

+ Urška Sršen — Bellabeat’s cofounder and Chief Creative Officer

+ Sando Mur — Mathematician and Bellabeat’s cofounder; key member of the Bellabeat executive team

+ Bellabeat marketing analytics team — A team of data analysts responsible for collecting, analyzing, and reporting data that helps guide Bellabeat’s marketing strategy.

##### Prepare:

Data that will be collected and used the is **FitBit Fitness Tracker** data gotten from Kaggle. These 18 data sets
contain personal fitness tracker from thirty fitbit users. Thirty eligible Fitbit users consented to the submission of
personal tracker data, including minute-level output for physical activity, heart rate, and sleep monitoring. It includes
information about daily activity, steps, and heart rate that can be used to explore users’ habits.

Considering that bellabeat creates products for women only, the data collected has limitations such as a small sample size of thirty participants. The key factors as well are limited and missing values like age, gender, location and lifestyle choices.

The datasets that will be used for Analysis are Daily activity, daily calories, daily intensities, daily steps, sleep and weight.

Rstudio is also used to perform this analysis due to the numerous datasets being used and for simplicity

##### Installing and Loading Packages

```{r}
install.packages("tidyverse")
install.packages("dpylr")
install.packages("janitor")
install.packages("readr")

library(tidyverse)  
library(dpylr)  
library(janitor)  
library(readr)  
```
##### Importing Datasets

```{r}
setwd("~/Desktop/bellabeat data")
dailyCalories_merged <- read_csv("dailyCalories_merged.csv")
```





